---
title: "16 Girlnames from top 50"
author: "Sarah Nielsen & Anna Schmidt"
date: "26-05-2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## INSTALL PACKAGES.

```{r insrall}
#install.packages("tidyverse")
#install.packages("ggplot2", repos = "https://cran.rstudio.com/")
```

##LOAD PACKAGES.

```{r}
library(tidyverse)
library(ggplot2)
Girlnames<- read_csv("data/16_Girlnames.csv")
```


## RE-SHAPE THE DATA TYPE.

```{r,echo=FALSE}

#Re-name the first colume 
colnames(Girlnames)[1] <- "Name"  # this helps the program re-shape the format

#from wide to long format
long_data_G <- Girlnames %>%
  pivot_longer(
    cols = -Name,           # all columns except 'Name'
    names_to = "Year",
    values_to = "Count",
    values_drop_na = TRUE
  )

```
```{r}
# making Count numeric and replacing N/A with 0
long_data_G %>% 
  mutate(Count = str_replace(Count, "N/A", "0")) %>% 
  mutate(Count = as.numeric(Count)) -> long_data_G
```

## MAKING THE VISUALISATION
This code makes a individual VISAUALISATION for all 16 Girl names, and places them side by side.
```{r}
  long_data_G %>% 
  mutate(Year = as.numeric(Year)) %>%
  ggplot( aes(x = Year, y = Count, group = Name)) +
  geom_line() +
  facet_wrap(~ Name, scales = "fixed") +
  scale_x_continuous(breaks = seq(1993, 2020, by = 5)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
   aes(colour = Name)+
  labs(title = "16 girl names from top 50 over time", x = "Years (1993-2020)", y = "Count per 1000")
```
## USED WHEN WANTING TO LOOK AT ONE SPESIFIC NAME
Following code is used to look at names one at a time. It can be used for all 16 names, one just need to change the name in the filter (Name %in% c()) code.
```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Saga")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Saga ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Karla")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Karla", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Luna")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Luna", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Amalie")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Amalie", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Anna")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Anna ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Esther")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Esther ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Freja")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Freja ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Ida")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Ida ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Isabella")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Isabella ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Josephine/Josefine")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Joesphine/Josefine ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Laura")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Laura ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Maja")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Maja ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Marie")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Marie ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Nadia")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Nadia ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Natasja/Natasha")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Natasja/Natasha ", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Sara/Sarah")) %>%   #used to get a plot for a specific name
  ggplot(aes(x = Year, y = Count, group = Name)) +
  geom_area(fill = "red", alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  facet_wrap(~ Name) +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Popularity trend for Girl name: Sara/Sarah ", x = "Years (1993-2020)", y = "Count per 1000")
```




## USED TO COMPARE TWO ORE MORE NAMES.
This code is used when one want to compare more names. One fill the filter (Name %in% c()) code with the names one want to observe.
```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Saga", "Karla", "Amalie")) %>%   #Includes 3 names
  ggplot(aes(x = Year, y = Count, group = Name, colour = Name, fill = Name)) +
  geom_area(alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Trends in selected pop-culture girl names from Top 50", x = "Years (1993-2020)", y = "Count per 1000")
```


```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Anna", "Sara/Sarah", "Marie")) %>%   #Includes 3 names
  ggplot(aes(x = Year, y = Count, group = Name, colour = Name, fill = Name)) +
  geom_area(alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Trends in selected Biblical girl names from Top 50", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Isabella", "Josephine/Josefine")) %>%   #Includes 2 names
  ggplot(aes(x = Year, y = Count, group = Name, colour = Name, fill = Name)) +
  geom_area(alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Trends in selected Royal girl names from Top 50", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Maja", "Laura", "Ida","Freja")) %>%   #Includes 2 names
  ggplot(aes(x = Year, y = Count, group = Name, colour = Name, fill = Name)) +
  geom_area(alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Trends in selected Generational girl names from Top 50", x = "Years (1993-2020)", y = "Count per 1000")
```

```{r}
long_data_G %>%
  mutate(Year = as.numeric(Year)) %>%
  filter(Name %in% c("Natasja/Natasha", "Nadia", "Esther")) %>%   #Includes 2 names
  ggplot(aes(x = Year, y = Count, group = Name, colour = Name, fill = Name)) +
  geom_area(alpha = 0.2, position = "identity") +  # Colored area with some transparency
  geom_line() +
  scale_x_continuous(breaks = seq(1993, 2020, by = 2)) +
  scale_y_continuous(limits = c(0, 30), breaks = seq(0, 30, by = 5)) +  # ensures consistency
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  aes(colour = Name)+
  labs(title = "Trends in selected girl names from Top 50", x = "Years (1993-2020)", y = "Count per 1000")
```




